Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Start fixing truncated decimals

                           &  $1$  & $5.772454$ & $5.772454$ & $5.772454$ \\
                           &  $2$  & $5.772454$ & $5.671234$ & $5.671234$ \\
                           &  $3$  & $5.679048$ & $5.658272$ & $5.553528$ \\
                           &  $4$  & $5.679048$ & $5.631669$ & $5.534333$ \\
                           &  $5$  & $5.677282$ & $5.622092$ & $5.523490$ \\
    \multirow{2}{*}{$2.0$} &  $6$  & $5.677282$ & $5.613118$ & $5.517552$ \\
                           &  $7$  & $5.677206$ & $5.608130$ & $5.513709$ \\
                           &  $8$  & $5.677206$ & $5.604026$ & $5.511012$ \\
                           &  $9$  & $5.677204$ & $5.601216$ & $5.509050$ \\
                           &  $10$ & $5.677204$ & $5.598946$ & $5.507540$ \\
                           &  $11$ & $5.677204$ & $5.597213$ & $5.506356$ \\
                           &  $12$ & $5.677204$ & $5.595791$ & $5.505399$ \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  $2$  & $4.864244$ & $4.864244$ & $4.864244$ \\
                         &  $3$  & $4.435740$ & \nan & $4.319901$ \\
                         &  $4$  & $4.019787$ & \nan & $3.829962$ \\
                         &  $5$  & $3.963149$ & \nan & $3.666722$ \\
  \multirow{2}{*}{$0.1$} &  $6$  & $3.870617$ & \nan & $3.597876$ \\
                         &  $7$  & $3.863135$ & \nan & $3.590388$ \\
                         &  $8$  & $3.852880$ & \nan & $3.587711$ \\
                         &  $9$  & $3.852591$ & \nan & $3.587291$ \\
                         &  $10$ & $3.852393$ & \nan & $3.587136$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $13.640713$ & $13.640713$ & $13.640713$ \\
                         &  $3$  & $13.051620$ & $13.385987$ & $12.901520$ \\
                         &  $4$  & $12.357471$ & $13.261097$ & $12.057345$ \\
                         &  $5$  & $12.325128$ & $13.138572$ & $11.934988$ \\
  \multirow{2}{*}{$0.5$} &  $6$  & $12.271499$ & $13.084158$ & $11.864098$ \\
                         &  $7$  & $12.271375$ & $13.068399$ & $11.849762$ \\
                         &  $8$  & $12.271361$ & $13.055561$ & $11.841330$ \\
                         &  $9$  & $12.271337$ & $13.045386$ & $11.835470$ \\
                         &  $10$ & $12.271326$ & $13.037878$ & $11.831351$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $22.219813$ & $22.219813$ & $22.219813$ \\
                         &  $3$  & $21.593198$ & $21.974675$ & $21.423811$ \\
                         &  $4$  & $20.766919$ & $21.854191$ & $20.429265$ \\
                         &  $5$  & $20.748402$ & $21.793624$ & $20.332454$ \\
  \multirow{2}{*}{$1.0$} &  $6$  & $20.720257$ & $21.750091$ & $20.274013$ \\
                         &  $7$  & $20.720132$ & $21.718843$ & $20.249849$ \\
                         &  $8$  & $20.719248$ & $21.695224$ & $20.234705$ \\
                         &  $9$  & $20.719248$ & $21.675931$ & $20.224389$ \\
                         &  $10$ & $20.719217$ & $21.661830$ & $20.21707530$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $37.281425$ & $37.281425$ & $37.281425$ \\
                         &  $3$  & $36.637217$ & $37.042127$ & $36.450634$ \\
                         &  $4$  & $35.689555$ & $36.925664$ & $35.328432$ \\
                         &  $5$  & $35.681729$ & $36.864367$ & $35.250185$ \\
  \multirow{2}{*}{$2.0$} &  $6$  & $35.672333$ & $36.812895$ & $35.200308$ \\
                         &  $7$  & $35.671851$ & $36.775986$ & $35.168245$ \\
                         &  $8$  & $35.670358$ & $36.747864$ & $35.147097$ \\
                         &  $9$  & $35.670333$ & $36.725261$ & $35.131953$ \\
                         &  $10$ & $35.670144$ & $36.708362$ & $35.121033$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N6}
    \end{table}

    \begin{table}
        \centering
        \caption{Here we look at $N = 12$ particles ($R = 3$ shells).  We did
        not achieve convergence using the harmonic oscillator basis for the
        lower frequency values and large number of shells.}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                      & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                      & $4$ & $43.663266$ & $45.837079$ & $43.309845$ \\
                      & $5$ & $41.108850$ & $45.456882$ & $40.654709$ \\
                      & $6$ & $40.750512$ & \nan & $40.068340$ \\
                $0.5$ & $7$ & $40.302718$ & \nan & $39.508500$ \\
                      & $8$ & $40.263751$ & \nan & $39.399128$ \\
                      & $9$ & $40.216688$ & \nan & $39.329310$ \\
                      & $10$ & $40.216251$ & \nan & $39.309409$ \\
                      & $11$ & $40.216194$ & \nan & $39.296007$ \\
                      & $12$ & $40.216165$ & \nan & $39.285968$ \\
                \hline
                      & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                      & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                      & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                      & $6$ & $67.296869$ & \nan & $66.526677$ \\
                $1.0$ & $7$ & $66.934744$ & \nan & $66.049564$ \\
                      & $8$ & $66.923094$ & \nan & $65.972157$ \\
                      & $9$ & $66.912244$ & \nan & $65.921204$ \\
                      & $10$ & $66.912035$ & \nan & $65.889281$ \\
                      & $11$ & $66.911364$ & \nan & $65.866715$ \\
                      & $12$ & $66.911364$ & \nan & $65.849775$ \\
                \hline
                      & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                      & $4$ & $117.339641$ & $120.299999$ & $116.995036$ \\
                      & $5$ & $113.660396$ & $120.012284$ & $113.048934$ \\
                      & $6$ & $113.484866$ & $119.872007$ & $112.658821$ \\
                $2.0$ & $7$ & $113.247601$ & $119.662201$ & $112.309482$ \\
                      & $8$ & $113.246578$ & $119.584733$ & $112.235521$ \\
                      & $9$ & $113.246302$ & $119.524417$ & $112.181828$ \\
                      & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                      & $11$ & $113.245255$ & $119.430435$ & $112.109972$ \\
                      & $12$ & $113.245183$ & $119.394712$ & $112.085683$ \\
                \hline
                $5.0$ & $3$ & $242.334878$ & $242.334878$ & $242.334878$ \\
                      & $4$ & $238.739590$ & $241.927593$ & $238.394598$ \\
                      & $5$ & $234.352741$ & $241.663950$ & $233.680649$ \\
                      & $6$ & $234.282331$ & $241.507595$ & $233.425243$ \\
                      & $7$ & $234.194820$ & $241.390524$ & $233.226529$ \\
                      & $8$ & $234.194058$ & $241.293416$ & $233.137932$ \\
                      & $9$ & $234.190796$ & $241.221056$ & $233.070206$ \\
                      & $10$ & $234.190714$ & $241.158896$ & $233.020009$ \\
                      & $11$ & $234.190665$ & $241.109926$ & $232.980634$ \\
                      & $12$ & $234.190552$ & $241.068091$ & $232.948528$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}
    \end{table}

>>>>

                           &  $1$  & $5.772454$ & $5.772454$ & $5.772454$ \\
                           &  $2$  & $5.772454$ & $5.671234$ & $5.671234$ \\
                           &  $3$  & $5.679048$ & $5.658272$ & $5.553528$ \\
                           &  $4$  & $5.679048$ & $5.631669$ & $5.534333$ \\
                           &  $5$  & $5.677282$ & $5.622092$ & $5.523490$ \\
    \multirow{2}{*}{$2.0$} &  $6$  & $5.677282$ & $5.613118$ & $5.517552$ \\
                           &  $7$  & $5.677206$ & $5.608130$ & $5.513709$ \\
                           &  $8$  & $5.677206$ & $5.604026$ & $5.511012$ \\
                           &  $9$  & $5.677204$ & $5.601216$ & $5.509050$ \\
                           &  $10$ & $5.677204$ & $5.598946$ & $5.507540$ \\
                           &  $11$ & $5.677204$ & $5.597213$ & $5.506356$ \\
                           &  $12$ & $5.677204$ & $5.595791$ & $5.505399$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  $2$  & $4.864244$ & $4.864244$ & $4.864244$ \\
                         &  $3$  & $4.435740$ & $4.446235$ & $4.319901$ \\
                         &  $4$  & $4.019787$ & $4.383692$ & $3.829962$ \\
                         &  $5$  & $3.963149$ & \nan & $3.666722$ \\
                         &  $6$  & $3.870617$ & \nan & $3.597876$ \\
                  $0.1$  &  $7$  & $3.863135$ & \nan & $3.590388$ \\
                         &  $8$  & $3.852880$ & \nan & $3.587711$ \\
                         &  $9$  & $3.852591$ & \nan & $3.587291$ \\
                         &  $10$ & $3.852393$ & \nan & $3.587136$ \\
                         &  $11$ & $3.852391$ & \nan & $3.586821$ \\
                         &  $12$ & $3.852382$ & \nan & $3.586582$ \\ \hline

                         &  $2$  & $13.640713$ & $13.640713$ & $13.640713$ \\
                         &  $3$  & $13.051620$ & $13.385987$ & $12.901520$ \\
                         &  $4$  & $12.357471$ & $13.261097$ & $12.057345$ \\
                         &  $5$  & $12.325128$ & $13.138572$ & $11.934988$ \\
                         &  $6$  & $12.271499$ & $13.084158$ & $11.864098$ \\
                  $0.5$  &  $7$  & $12.271375$ & $13.068399$ & $11.849762$ \\
                         &  $8$  & $12.271361$ & $13.055561$ & $11.841330$ \\
                         &  $9$  & $12.271337$ & $13.045386$ & $11.835470$ \\
                         &  $10$ & $12.271326$ & $13.037878$ & $11.831351$ \\
                         &  $11$ & $12.271324$ & \nan & $11.828242$ \\
                         &  $12$ & $12.271320$ & \nan & $11.825835$ \\ \hline

                         &  $2$  & $22.219813$ & $22.219813$ & $22.219813$ \\
                         &  $3$  & $21.593198$ & $21.974675$ & $21.423811$ \\
                         &  $4$  & $20.766919$ & $21.854191$ & $20.429265$ \\
                         &  $5$  & $20.748402$ & $21.793624$ & $20.332454$ \\
                         &  $6$  & $20.720257$ & $21.750091$ & $20.274013$ \\
                  $1.0$  &  $7$  & $20.720132$ & $21.718843$ & $20.249849$ \\
                         &  $8$  & $20.719248$ & $21.695224$ & $20.234705$ \\
                         &  $9$  & $20.719248$ & $21.675931$ & $20.224389$ \\
                         &  $10$ & $20.719217$ & $21.661830$ & $20.217075$ \\
                         &  $11$ & $20.719215$ & $21.649812$ & $20.211541$ \\
                         &  $12$ & $20.719215$ & $21.640765$ & $20.207258$ \\
                         \hline

                         &  $2$  & $37.281425$ & $37.281425$ & $37.281425$ \\
                         &  $3$  & $36.637217$ & $37.042127$ & $36.450634$ \\
                         &  $4$  & $35.689555$ & $36.925664$ & $35.328432$ \\
                         &  $5$  & $35.681729$ & $36.864367$ & $35.250185$ \\
                         &  $6$  & $35.672333$ & $36.812895$ & $35.200308$ \\
                  $2.0$  &  $7$  & $35.671851$ & $36.775986$ & $35.168245$ \\
                         &  $8$  & $35.670358$ & $36.747864$ & $35.147097$ \\
                         &  $9$  & $35.670333$ & $36.725261$ & $35.131953$ \\
                         &  $10$ & $35.670144$ & $36.708362$ & $35.121033$ \\
                         &  $11$ & $35.670143$ & $36.694188$ & $35.112680$ \\
                         &  $12$ & $35.670127$ & $36.683281$ & $35.106188$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N6}
    \end{table}

    \begin{table}
        \centering
        \caption{Here we look at $N = 12$ particles ($R = 3$ shells).  We did
        not achieve convergence using the harmonic oscillator basis for the
        lower frequency values and large number of shells.}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                      & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                      & $4$ & $43.663267$ & $45.837079$ & $43.309845$ \\
                      & $5$ & $41.108851$ & $45.456883$ & $40.654710$ \\
                      & $6$ & $40.750512$ & \nan & $40.068340$ \\
                $0.5$ & $7$ & $40.302719$ & \nan & $39.508500$ \\
                      & $8$ & $40.263752$ & \nan & $39.399128$ \\
                      & $9$ & $40.216688$ & \nan & $39.329311$ \\
                      & $10$ & $40.216252$ & \nan & $39.309409$ \\
                      & $11$ & $40.216195$ & \nan & $39.296007$ \\
                      & $12$ & $40.216165$ & \nan & $39.285968$ \\
                \hline
                      & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                      & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                      & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                      & $6$ & $67.296869$ & \nan & $66.526677$ \\
                $1.0$ & $7$ & $66.934745$ & \nan & $66.049564$ \\
                      & $8$ & $66.923094$ & \nan & $65.972157$ \\
                      & $9$ & $66.912244$ & \nan & $65.921205$ \\
                      & $10$ & $66.912035$ & \nan & $65.889281$ \\
                      & $11$ & $66.911365$ & \nan & $65.866715$ \\
                      & $12$ & $66.911364$ & \nan & $65.849776$ \\
                \hline
                      % NO FURTHER!
                      & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                      & $4$ & $117.339641$ & $120.299999$ & $116.995036$ \\
                      & $5$ & $113.660396$ & $120.012284$ & $113.048934$ \\
                      & $6$ & $113.484866$ & $119.872007$ & $112.658821$ \\
                $2.0$ & $7$ & $113.247601$ & $119.662201$ & $112.309482$ \\
                      & $8$ & $113.246578$ & $119.584733$ & $112.235521$ \\
                      & $9$ & $113.246302$ & $119.524417$ & $112.181828$ \\
                      & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                      & $11$ & $113.245255$ & $119.430435$ & $112.109972$ \\
                      % TODO: You were here going upwards ^
                      & $12$ & $113.245183$ & $119.394712$ & $112.085683$ \\
                \hline
                $5.0$ & $3$ & $242.334878$ & $242.334878$ & $242.334878$ \\
                      & $4$ & $238.739590$ & $241.927593$ & $238.394598$ \\
                      & $5$ & $234.352741$ & $241.663950$ & $233.680649$ \\
                      & $6$ & $234.282331$ & $241.507595$ & $233.425243$ \\
                      & $7$ & $234.194820$ & $241.390524$ & $233.226529$ \\
                      & $8$ & $234.194058$ & $241.293416$ & $233.137932$ \\
                      & $9$ & $234.190796$ & $241.221056$ & $233.070206$ \\
                      & $10$ & $234.190714$ & $241.158896$ & $233.020009$ \\
                      & $11$ & $234.190665$ & $241.109926$ & $232.980634$ \\
                      & $12$ & $234.190552$ & $241.068091$ & $232.948528$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}
    \end{table}
